### 2015-01-16 publishing/plos_template.tex
spell checked and commented out rest of 3-inch

Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, 
although printing materials have been limited to non­oxygen permeable materials.
We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
%Two devices are presented and characterized.

@@

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
Recently 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014} (spence). 
Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
We demonstrate a device that nests into a 24 well culture plate.
%Two devices are demonstrated: an open-well petri dish design and a device that nests into a 24 well culture plate.

@@

%The 3-inch (75 mm) petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
%The 3D part is printed with the channels embedded in the bottom of the petri dish. 
%A 120 $\mu$m thick PDMS membrane is adhered across the channels by spin coating a thin layer of PDMS on the membrane and allowing it to cure in place.
%The device is designed so that a standard 3” petri dish lid may be used.
%This device allows cell culture in a large open well format compatible with assays requiring cell scraping.
%The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be repaced with a new membrane to reuse the device.

The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24 well plate. 
The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs to simplify device operation.
The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.
Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{device-photos-figure}.

@@

Oxygen was measured with PtOEPK planar sensors that were fixed to the bottom of a 24well plate. 
The intensity of the sensor was measured and corellated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
Gas was perfused through the device with negitave pressure to eliminate bubbles.
The inlet tubing was placed in a cone with with a flow that exceded the vacuum flow rate.
All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments.

@@

Oxygen was measured in the 3” petri dish device with a commercial fiber­optic probe (Figure 2).
Oxygen control was demonstrated with gas flowing through the channel under the PDMS membrane.

>>>>

Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, 
although printing materials have been limited to non-oxygen permeable materials.
We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
%Two devices are presented and characterized.

@@

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
Recently 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014}. 
Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
We demonstrate a device that nests into a 24 well culture plate.
%Two devices are demonstrated: an open-well petri dish design and a device that nests into a 24 well culture plate.

@@

%The 3-inch (75 mm) petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
%The 3D part is printed with the channels embedded in the bottom of the petri dish. 
%A 120 $\mu$m thick PDMS membrane is adhered across the channels by spin coating a thin layer of PDMS on the membrane and allowing it to cure in place.
%The device is designed so that a standard 3” petri dish lid may be used.
%This device allows cell culture in a large open well format compatible with assays requiring cell scraping.
%The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be replaced with a new membrane to reuse the device.

The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24 well plate. 
The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs to simplify device operation.
The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{device-photos-figure}.

@@

Oxygen was measured with PtOEPK planar sensors that were fixed to the bottom of a 24 well plate. 
The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
Gas was perfused through the device with negative pressure to eliminate bubbles.
The inlet tubing was placed in a cone with with a flow that exceed the vacuum flow rate.
All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments.

@@

%Oxygen was measured in the 3” petri dish device with a commercial fiber­optic probe (Figure 2).
%Oxygen control was demonstrated with gas flowing through the channel under the PDMS membrane.
